Naturalness and Long-Lived Beyond the Standard Model Particles

### 2017-08-04 tex/draft.tex
Add draft

\begin{abstract}

I'll write an abstract here.

>>>>

\begin{abstract}
    In the standard model, the mass of the Higgs boson is unnaturally small. Beyond the standard model (BSM) theories, such as supersymmetry, explain the smallness of the Higgs boson mass while also predicting new phenomena that could potentially be observed at the Large Hadron Collider (LHC). As natural BSM models are increasingly constrained by null results, it becomes important to identify signals that would be missed in conventional analyses, such as long-lived BSM particles. This paper explores the motivation for natural BSM theories that predict long-lived particles, provides an overview of the CMS detector, reviews several recent long-lived particle searches, and discusses the current status and future prospects of natural BSM models.
